Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-12 blind.tex
Start action items on blindness compiler

@@

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval(pk, \cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec(sk_{t-1}, \ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching its encryption key;
				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypts the old encryption by \linebreak
				$$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t}).$$
				Then it applies the next-message function homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec(sk_T, \ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
	In $\Hyb_i$, we modify $(\Pblind, \Vblind(x))$ s.t.
	for all rounds associated with $\cV{t}$ where $t\geq i$, the verifier replaces the $\ctx{sk}{t-1}{t}$ in its message with encryption of $0$.
	Then, for all $t$, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
	By applying triangle inequality iteratively\Ethan{Is this enough or do we need equations?}, we obtain that $\Hyb_1$ is indistinguishable with $\Hyb_{T+1}$.
	Since $\Hyb_{T+1}$ is precisely $\Piblind$, and $\Hyb_1$ is clearly blind, we conclude that $\Piblind$ is blind.
\end{proof}

This compiler implies a relatively simple way to create a blind and constant-round delegation protocol with a classical client for $\BQP$, with negligible soundness and completeness errors.
To do so, apply it to the protocol from \cite{parallelrep, alagic2019twomessage}.
Similarly, the compiler can be applied to our $\FBQP$ and $\SampBQP$ protocols \Ethan{TODO name} too.

>>>>

\Ethan{How to work the security parameter into the following? It's annoying if everything takes that.
Also, where do I write that footnote about extra uncompiled inputs such as accuracy param.?}

@@

	\begin{enumerate}
		\item $\Vblind$ generates $(v_1, st_{V, 1})\leftarrow\cV_1(x)$.
			Then it generates $(pk_1, sk_1)\leftarrow\QGen(1^\lambda, 1^L)$,
			and encrypts $\ctx{x}{}{1}\leftarrow\QEnc(pk_1, x)$ and $\ctx{v}{1}{1}\leftarrow\QEnc(pk_1, v_1)$.
			It sends $pk_1$, $\ctx{x}{}{1}$, and $\ctx{v}{1}{1}$ to the prover.
		\item $\Pblind$ generates $(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\cPblind{1}(\ctx{v}{1}{1}, \ctx{x}{}{1})$
			by evaluating \linebreak
			$(\ctx{p}{1}{1}, \ctx{st}{P, 1}{1})\leftarrow\QEval(pk, \cP_1, \ctx{v}{1}{1}, \ctx{x}{}{1})$.
			It sends $\ctx{p}{1}{1}$ to the verifier.
		\item for $t=2,\ldots,T$:
		\begin{enumerate}
			\item $\Vblind$ decrypts the prover's last message by $p_{t-1}\leftarrow\QDec(sk_{t-1}, \ctx{p}{t-1}{t-1})$,
				then generates $(v_t, st_{V, t})\leftarrow\cV_t(p_{t-1}, st_{V, t-1})$.
				Then it generates $(pk_t, sk_t)\leftarrow\QGen(1^\lambda, 1^L)$,
				and produces encryptions $\ctx{v}{t}{t}\leftarrow\QEnc(pk_t, v_t)$ and $\ctx{sk}{t-1}{t}\leftarrow\QEnc(pk_t, sk_{t-1})$.
				It sends $pk_t$, $\ctx{v}{t}{t}$, and $\ctx{sk}{t-1}{t}$ to the prover.
			\item $\Pblind$ generates $(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\cPblind{t}(\ctx{v}{t}{t}, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1})$
				by first switching its encryption key;
				that is, it encrypts its state under the new key by $\ctx{st}{P, t-1}{t-1, t}\leftarrow\QEnc(pk_t, \ctx{st}{P, t-1}{t-1}))$,
				then homomorphically decrypts the old encryption by \linebreak
				$\ctx{st}{P, t-1}{t}\leftarrow\QEval(pk_t, \QDec, \ctx{sk}{t-1}{t}, \ctx{st}{P, t-1}{t-1, t}).$
				Then it applies the next-message function homomorphically, generating
				$(\ctx{p}{t}{t}, \ctx{st}{P, t}{t})\leftarrow\QEval(pk_t, \cP_t, \ctx{v}{t}{t}, \ctx{st}{P, t-1}{t})$.
				It sends $\ctx{p}{t}{t}$ back to the verifier.
		\end{enumerate}
		\item $\Vblind$ decrypts the prover's final message by $p_T\leftarrow\QDec(sk_T, \ctx{p}{T}{T})$.
			It then computes its output $o\leftarrow\cV_{out}(p_T, st_{V, T})$.
	\end{enumerate}
\end{protocol}

@@

Finally, we show the blindness of $\Piblind$ through a standard hybrid argument:
\begin{theorem}
	$\Piblind$ is blind.
\end{theorem}
\begin{proof}
	Consider $T+1$ hybrids experiments, from $\Hyb_1$ to $\Hyb_{T+1}$.
	We define $\Hyb_{T+1}$ to be $\Piblind$.
	For $t<T+1$, we define $\Hyb_{t}$ to be the same as $\Hyb_{t+1}$,
	except when $\Vblind$ should send $\ctx{sk}{t}{t}$, it instead sends $\ctx{0}{}{t}$ which is encryption of $0$ under $pk_t$.
	Then, for all $t$, from the perspective of the prover, $\Hyb_{t+1}$ is computationally indistinguishable from $\Hyb_t$ due to the CPA security of $\QHE$ under $pk_t$.
	By applying triangle inequality iteratively \Ethan{good enough?}, we observe that $\Hyb_1$ is computationally indistinguishable with $\Hyb_{T+1}$.
	Furthermore, $\Hyb_1$ is blind since the prover isn't provided any information about any secret keys.
	So we conclude that $\Piblind$ is blind.
\end{proof}

Our compiler is a straightforward way of achievement blindness with existing $\QPIP_0$ protocols while preserving other runtime properties.
In particular, we now apply it to the delegation protocol for $\BQP$ from \cite{parallelrep, alagic2019twomessage},
as well as our $\SampBQP$ protocol $\PiSamp$ to obtain the following results respectively.

\begin{theorem}
	There exists a blind, constant-round $\QPIP_0$ protocol for $\BQP$ with negligible completeness and soundness errors.
\end{theorem}

\begin{theorem}
	There exists a computationally sound, blind, and constant-round $\QPIP_0$ protocol for $\SampBQP$ with negligible completeness errors.
\end{theorem}
